Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-16 Ben_Manuscripts/Masters_Bypass/methods.tex
edits

The timescale for self assembly of monomers into the hexagonal phase is
unknown and likely outside of a reasonable length for an atomistic
simulation, calling for a more efficient way to build the system. 
Previous work has shown a coarse grain model self assemble into the HII
phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
Atomistic self-assembly was attempted by packing monomers into a box 
using Packmol\cite{martinez_packmol:_2009}. Simulations of $>$ 100 ns 
show no indicators of progress towards an ordered system. To bypass the
slow self-assembly process, python scripts are used to assemble 
monomers into a structure close to the expected equilibrium configuration.
A short, restrained equilibration, followed by NPT simulations $>$ 500 ns, 
allows the initial configuration to relax into an equilibrium configuration.
Our logic for choosing a starting configuration and the details of the equilibration 
schemes are presented below. % eliminate this sentence?
% Unit Cell building method and justification

>>>>

The timescale for self assembly of monomers into the hexagonal phase is
unknown and likely outside of a reasonable length for an atomistic
simulation, calling for a more efficient way to build the system. 
Previous work has shown a coarse grain model self assemble into the HII
phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
Atomistic self-assembly was attempted by packing monomers into a box 
using Packmol\cite{martinez_packmol:_2009}. Simulations of $>$ 100 ns 
show no indicators of progress towards an ordered system. To bypass the
slow self-assembly process, python scripts are used to assemble 
monomers into a structure close to the expected equilibrium configuration (Fig~\ref{fig:python})
A short, restrained equilibration, followed by NPT simulations $>$ 500 ns, 
allows the initial configuration to relax into an equilibrium configuration.
Our logic for choosing a starting configuration and the details of the equilibration 
schemes are presented below. % eliminate this sentence?
% Unit Cell building method and justification

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{build.PNG}
	\caption{(a) Single monomers are parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and place in a monoclinic unit cell}\label{fig:python}
\end{figure}

### 2017-08-16 Ben_Manuscripts/Masters_Bypass/results.tex
edits

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\centering
		\includegraphics[width=\linewidth, valign=t]{WAXS_soft_confined.png}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}{0.43\linewidth}
		\centering
		\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{figs:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart (b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
\end{figure}
